The function--sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-08 dictionary.tex
Working on Aut for finite QCS

Later in the paper we will make a study of isomorphism classes of objects in $\rfQC{G}$. Here we focus on morphisms in this category.

@@

\begin{proof}
Trivial morphisms in $\rfQC(G)$ are defined as follows. Let $(f,\psi,r)$ and $(f_1,\psi_1,r_1)$ be finite quasicharacter sheaves on $G$.  
Form $(f\times_G f_1,1\otimes \psi_1, r\otimes r_1)$ in $C_1(G)$. 
Let $0 : V \to V\otimes V_1$ be the trivial linear transformation. 
Choose $0\ne v \in V$ and let $T_v: V_1 \to V\otimes V_1$ be the isomorphism $T_v(v_1) = v\otimes v_1$.  
Let $\pi : H\times_G H_1 \to H$ and $\pi_1 : H\times_G H_1 \to H_1$ be the natural projections.
Then $(\pi,0) : (f,\psi, V) \to  (f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ is a morphism in $C_1(G)$ and $(\pi_1,T_v) : (f_1,\psi_1,V_1) \to (f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ is a weak isomorphism in $C_1(G)$.
%
The morphism in $\rfQC(G)$ represented by
\[
\begin{tikzcd}[column sep=30]
   (f,\psi,V) \arrow{r}{(\pi,0)} & (f\times_G f_1,1\otimes \psi_1, V\otimes V_1) & \arrow[swap]{l}{(\pi_1,T_v)}[swap]{\text{w-iso}}  (f_1,\psi_1,V_1),
   \end{tikzcd}
\]
does not depend on the choice of $0\ne v\in V$; this defines the {\em trivial morphism} $0: (f,\psi,V) \to (f_1,\psi_1,V_1)$ in $\rfQC(G)$.

>>>>

Later in the paper we will make a study of isomorphism classes of objects in $\rfQC(G)$. Here we focus on morphisms in this category.

@@

\begin{proof}
\todo{This proof is under construction.}
Trivial morphisms in $\rfQC(G)$ are defined as follows. Let $(f,\psi,r)$ and $(f_1,\psi_1,r_1)$ be finite quasicharacter sheaves on $G$.  
Form $(f\times_G f_1,1\otimes \psi_1, r\otimes r_1)$ in $C_1(G)$. 
Let $0 : V \to V\otimes V_1$ be the trivial linear transformation. 
Choose $0\ne v \in V$ and let $T_v: V_1 \to V\otimes V_1$ be the isomorphism $T_v(v_1) = v\otimes v_1$.  
Let $\pi : H\times_G H_1 \to H$ and $\pi_1 : H\times_G H_1 \to H_1$ be the natural projections.
Then $(\pi,0) : (f,\psi, V) \to  (f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ is a morphism in $C_1(G)$ and $(\pi_1,T_v) : (f_1,\psi_1,V_1) \to (f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ is a weak isomorphism in $C_1(G)$.
%
The morphism in $\rfQC(G)$ represented by
\[
\begin{tikzcd}[column sep=30]
   (f,\psi,V) \arrow{r}{(\pi,0)} & (f\times_G f_1,1\otimes \psi_1, V\otimes V_1) & \arrow[swap]{l}{(\pi_1,T_v)}[swap]{\text{w-iso}}  (f_1,\psi_1,V_1),
   \end{tikzcd}
\]
does not depend on the choice of $0\ne v\in V$; this defines the {\em trivial morphism} $0: (f,\psi,V) \to (f_1,\psi_1,V_1)$ in $\rfQC(G)$.
